E Coli project paper

### 2013-07-15 paper/paper.tex
paper changes

\documentclass[letterpaper,twocolumn,amsmath,amssymb,pre]{revtex4-1}
\usepackage{graphicx}% Include figure files
\usepackage{dcolumn}% Align table columns on decimal point
\usepackage{bm}% bold math
\usepackage{color}
\usepackage{breqn}

@@

\section{Randst shape}
There are sudden bursts in the nflE protein plots, at the poles. Their
density maxima build very quickly then diffuse more slowly.

The star shape (randst-96) Shows oscillations in nflD horizontally,
two poles to two poles.  There is sometimes a small amount of lag
between the upper maxima moving horizontally and the lower.  Half
periods take roughly 25s. Dimensions are roughly 5.00 by 5.00?  Check
this.  The nflE short bursts do develop lag between when the top and
the bottom go off.  Should coordinate this with the nflD lag.

Randst 97 nflE starts with small maxima, not much difference at all,
then actually builds to high maxima at the poles.

Randst 99 (sort of triangle) is roughly dimensions of 3.5 by 3.5?
nflD oscillations appear to be half periods of 25s as well.  Maxima appear
at the poles and in the interim there are weak maxima in center pole.

Funny randst shape 98 shows nflD oscillations of about 30s or so.

@@

\begin{figure}
  \includegraphics[width=\columnwidth]{../data/shape-randst/plots/time-map-compare-randst-10-60-60-990-150.pdf}
  \caption{randst 99}
  %\label{}
\end{figure}
\begin{figure}
  \includegraphics[width=\columnwidth]{../data/shape-randst/plots/time-map-compare-randst-10-80-60-980-150.pdf}
  \caption{randst 98}
  %\label{fig:pair-distribution-3}
\end{figure}
\begin{figure}
  \includegraphics[width=\columnwidth]{../data/shape-randst/plots/time-map-compare-randst-10-60-60-970-150.pdf}
  \caption{randst 97}
  %\label{fig:pair-distribution-3}
\end{figure}
\begin{figure}
  \includegraphics[width=\columnwidth]{../data/shape-randst/plots/time-map-compare-randst-10-60-60-960-150.pdf}
  \caption{randst 96}
  %\label{fig:pair-distribution-3}
\end{figure}

@@

>>>>

\documentclass[letterpaper,twocolumn,amsmath,amssymb,pre]{revtex4-1}
\usepackage{graphicx}% Include figure files
\usepackage{animate}
\usepackage{dcolumn}% Align table columns on decimal point
\usepackage{bm}% bold math
\usepackage{color}
\usepackage{breqn}

@@

\section{Randst shape}
whats the difference between the extremes in density at different
places (like the density max at the poles and at the rims in the
center).  Still need to do this.

There are sudden bursts in the nflE protein plots, at the poles. Their
density maxima build very quickly then diffuse more slowly.

\subsection{randst-96}
The star shape (randst-96) Shows oscillations in nflD horizontally,
two poles to two poles.  There is sometimes a small amount of lag
between the upper maxima moving horizontally and the lower.  Half
periods take roughly 25s. Dimensions are roughly 5.00 by 5.00?  Check
this.  The nflE short bursts do develop lag between when the top and
the bottom go off.  Should coordinate this with the nflD lag.

Tried to see if there is a time correlation between nflE and nflD but
the maxima seem to appear in the poles at roughly the same time.

Watched Nd and nE simulations next to each other at same time.  Both
have maxima that build up right at the walls (in the corners) and then
subside.  It's clear that the nE density bursts appear directly after
the Nd bursts.  The Nd bursts are subsiding as the nE bursts are
rising up.  The Nd reaches a time maxima just before the nE.  This is
true in each corner, so that when the maxima are lopsided top to
bottom - when the top right corner maximizes first, say, the interplay
between nE and Nd remains very clear in those corners where and when
maxima occur.

Watched nATP and nADP together.  nATP maxima seem to follow slightly
after nADP maxima.  This is not surprising since in rotation nATP
follows after nADP.  nATP maxima is more spread out - inbetween pole
maxima there is more spread out maxima in the center.  This should
show itself in the time map plotting.  About this - the percentage
difference seem to be the same between the non-max places and max
places, roughly, its just that the nATP seems to have a max region
that covers a wider area throughout the oscillation (or at least in
between the maxima points in the oscillation).

Also watched the Nd next to the nATP.  The Nd maximize more extreme in
the corners up against the walls.  The nATP density follows the Nd
maxima, it looks like the nATP maxima follows the Nd.  So if the Nd
appears somewhere (in a corner) then the nATP will travel there to
follow.

\subsection{randst-97}
Randst 97 nflE starts with small maxima, not much difference at all,
then actually builds to high maxima at the poles.
\subsection{randst-99}
Randst 99 (sort of triangle) is roughly dimensions of 3.5 by 3.5?
nflD oscillations appear to be half periods of 25s as well.  Maxima appear
at the poles and in the interim there are weak maxima in center pole.
\subsection{randst-98}
Funny randst shape 98 shows nflD oscillations of about 30s or so.

nADP and nATP side by side.  nADP maximizes in the corners right
before the nATP maxima follows.  Makes sense looking at equations.
Once again the nATP maxima is more spread out, where maxima in nADP
appear more just at walls.

Nd and nATP side by side.  Nd maximizes at walls and the nATP moves in
to follow it

Nd and nE side by side.  Nd maximizes in corners and then the nE also
maximizes in the corners.  The nE maxima appear in these sort of quick
bursts in the corners, along with a slower broader movements away from
that corner after the burst and into the next, where another sharp
burst occurs.  The Nd bursts occurs after the Nd as subsided in that
corner, and really by the time the burst maximizes, the Nd is already
on its way over and starting to build on the otehr side.

@@

%% \begin{figure}
%%   \includegraphics[width=\columnwidth]{../data/shape-randst/plots/time-map-compare-randst-10-60-60-990-150.pdf}
%%   \caption{randst 99}
%%   %\label{}
%% \end{figure}
%% \begin{figure}
%%   \includegraphics[width=\columnwidth]{../data/shape-randst/plots/time-map-compare-randst-10-80-60-980-150.pdf}
%%   \caption{randst 98}
%%   %\label{fig:pair-distribution-3}
%% \end{figure}
%% \begin{figure}
%%   \includegraphics[width=\columnwidth]{../data/shape-randst/plots/time-map-compare-randst-10-60-60-970-150.pdf}
%%   \caption{randst 97}
%%   %\label{fig:pair-distribution-3}
%% \end{figure}
%% \begin{figure}
%%   \includegraphics[width=\columnwidth]{../data/shape-randst/plots/time-map-compare-randst-10-60-60-960-150.pdf}
%%   \caption{randst 96}
%%   %\label{fig:pair-distribution-3}
%% \end{figure}

@@

\section{animate?}
\animategraphics[height=2.8in,autoplay,controls]{12}{../data/shape-randst/plots/movie-density-Nd-96/animate_}{0}{120}
